One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction

### 2017-01-11 Zhiyu.tex
Jan11 PRE format, tex

\bibliographystyle{apsrev4-1}
\usepackage{amsmath}
 \usepackage{amsfonts}
 \usepackage{amssymb}
 \usepackage{graphicx}
 \usepackage{subfigure}
 \usepackage{enumerate}
 \usepackage{verbatim}% for \begin{comment} \end{comment}
 \usepackage{color}
 \usepackage{xcolor}
 \usepackage{bm}
 \usepackage{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {red},
    citebordercolor = {green},
}
 \begin{document}
 \title{One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction}
 \author{Zhiyu}
 \affiliation{Fudan University, Shanghai, China}

@@

\section{Preparation}\label{section:preparation}
\subsection{Scaling behaviour}
We investigated the classical gas in harmonic trap with a repulsive interaction. We chose one of the simplest types of interaction:
\begin{equation}
F=\left\lbrace
\begin{aligned}
&F=F_0 	&,x\textless\sigma\\
&F=0 	&,x\textgreater\sigma
\end{aligned}
\right.
\label{eq:preparation1}
\end{equation}
so the Hamiltonian is
\begin{equation}
H=\frac{1}{2}m\omega_0^2\sum_{i}x_i^2+\frac{1}{2}m\sum_i v_i^2+\sum_{\left|x_i-x_j\right|\textless\sigma}F_0\left(\sigma-\left|x_i-x_j\right|\right)
\label{eq:preparation2}
\end{equation}
It can be shown that eq.\ref{eq:preparation2} can be rewrite into the following form:
\begin{equation}
\tilde{H}=\frac{1}{2}\sum_{i}\tilde{x_i}^2+\frac{1}{2}\sum_i\left(\frac{d\tilde{x}}{d\tilde{t}}\right)^2+\sum_{\left|\tilde{x_i}-\tilde{x_j}\right|\textless 1}F_0\left(1-\left|\tilde{x_i}-\tilde{x_j}\right|\right)
\end{equation}
with the transformation:
\begin{equation}
\left\lbrace
\begin{aligned}
&\tilde{H}&=&\frac{H}{m\omega_0^2\sigma^2}\\
&\tilde{x_i}&=&\frac{x_i}{\sigma}\\
&\tilde{t}&=&\omega_0t\\
&\tilde{F_0}&=&\frac{F_0}{m\omega_0^2\sigma}\\
\end{aligned}
\right.
\end{equation}

@@

\subsection{Overview}
\subsubsection{Relation between Radius and Energy}
The radius of the cloud R is defined as the root-mean-square of particles' position $\left\lbrace x_i\right\rbrace$. When E is very large, the interaction energy can be omitted, so E is dominated by the kinetic energy and potential energy of harmonic oscillators. Thus, $E=\omega_0^2\sum_{i}x_i^2=N\omega_0^2R^2$

\subsubsection{Ground states}
For the ground state of this system, one could predict that \\(1) When the $\sigma$ is larger than the size of the cloud (in view of the scaling behaviour, large $\sigma$ is equivalent to \textbf{small $\mathbf{F_0}$ limit} when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keeps an equal distance with its nearest neighbours, which is $\frac{2F_0}{\omega_0^2}$. The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When \textbf{$\mathbf{F_0}$ is very large} the molecules act like a hardcore gas, while the size of particle is just $\sigma$.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_GS_pre_2.eps}
\caption{particles' position at ground states }
\label{fig:GS1}
\end{figure}

@@

Since the number of particles we use in the Molecular Dynamics simulation is limited (usually 5 to 20), the random noise is significant. If we start with a state whose configuration in phase-space is an ellipse slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t). 
\begin{figure}[hbtp]
\center
\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log_2.eps}
\caption{breathing mode frequency measured at different E and $F_0$}
\label{fig:Breathingfrequency1}
\end{figure}

@@

Fig.\ref{fig:Breathingfrequency2} and Fig.\ref{fig:Breathingfrequency2_1} show this precession motion in the rotating frame in phase-space.

\begin{figure}
\centering
\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example2.eps} 
\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example1.eps} 
\caption{precession motion in phase-space observed in rotating frame (only show one(two) particles' trajectory in upper(lower) picture for clarity)}
\label{fig:Breathingfrequency2}
\end{figure}

\begin{figure*}
\subfigure[$t=0$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=1-5T.eps} 
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=1-5T.eps}
\end{minipage}
}
\subfigure[$t=\frac{1}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=2-5T.eps} 
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=2-5T.eps}
\end{minipage}
}\subfigure[$t=\frac{2}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=3-5T.eps} 
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=3-5T.eps}
\end{minipage}
}\subfigure[$t=\frac{3}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=4-5T.eps} 
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=4-5T.eps}
\end{minipage}
}\subfigure[$t=\frac{4}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=5-5T.eps} 
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=5-5T.eps}
\end{minipage}
}
\caption{N=50,F0=100,E=50000}
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=10T.eps} 
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=30T.eps}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=50T.eps} 
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=70T.eps}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=90T.eps} 
\caption{the precession behaviour of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
\label{fig:Breathingfrequency2_1}
\end{figure*}

\begin{figure}
\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_19trajectory_in_rotating_frame_t=130T_pre.eps}
\caption{the precession behaviour of cloud viewed in the rotating frame in phase-space, one snapshot in each 10 periods.}
\label{fig:Breathingfrequency2_2}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_scanE_pre.eps}
\caption{dependence of breathing frequency on Energy, N=20. Different color stands for different $F_0$: {\color{red}{Red}} for $F_0$=2000; {\color{yellow}{Yellow}} for $F_0$=3000; {\color{green}{Green}} for $F_0$=10000;  {\color{blue}{Blue}} for $F_0$=100000. Run with 3 different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles). The black dashed line is the prediction of eq.\ref{eq:breathingfrequency1}.}
\label{fig:Breathingfrequency4}
\end{figure}

The dependence of frequency on energy and $F_0$ is shown in fig.\ref{fig:Breathingfrequency4}. For the first thing, as expected when $F_0$ is high the frequency behaviour is well-described by linear prediction eq.\ref{eq:breathingfrequency1}. Secondly, the figure shows the frequency's dependence on $F_0$. As we explained, when $F_0$ is not so large, the precession angle decrease. In language of real space, the finite $F_0$ create a finite approaching time, thus consumes the time saved by finite-range collision. As a result, the frequency should be lower when $F_0$ decrease, and reach 2 earlier.

@@

\begin{figure}[hbtp]
\centering
%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
%\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_energydistribution_pre.eps} 
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=10_energydistribution_pre.eps} 
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_energydistribution_pre.eps}
\caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, {\color{green}{green}} curves corresponds to Boltzmann distribution; {\color{red}{red}} curves are obviously non-Boltzmann, while the {\color{yellow}{yellow}} ones are intermediate case, represent ``thermalization threshold". In three figures for different N, we choose E/N identical (=1000), and thermalization is reached at $F_0=500$-$F_0=1000$, which is consistent with our prediction in eq.\ref{eq:thermalizatiton condition}}
\label{fig:thermalization5}

@@

\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/11_1_boltzmann_N=10_F=10000_pre.eps}
\caption{Energy distribution, N=10, F0=10000}
\label{fig:thermalization9}

\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/11_1_boltzmann_N=20_F=10000_pre.eps} 
\caption{Energy distribution, N=20, F0=10000}
\label{fig:thermalization10}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_spectrum_N=10_E=1000_pre.eps}
\caption{Frequency spectrum, measured over $10^4$ time units.\label{fig:frequencyspectrum}}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_scanE_9_27_pre_screenshot.png}
\caption{LLE distribution for N=5, F0=1000, scan E.}
\label{fig:LLEdistribution1}
\end{figure}

@@

\begin{figure}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_1.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_2.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_3.png} 
\end{minipage}
}
\centering
\caption{Frequency of relative motion with internal energy in three regime} Numbers in the legend is the value of $\frac{F_0}{m\omega_0^2\sigma}$
\label{fig:thermalization3}
\end{figure}
\end{comment}
\cite{Dalfovo1997}
\cite{Tschischik2013}
\cite{Tschischik2015}
\cite{Guery-Odelin1999}
\cite{Yawn1997}
\cite{El-Zant1998}
\cite{Jin1996}
\cite{Tsuchiya2000}
\bibliography{mybib}

>>>>

\bibliographystyle{apsrev4-1}
\usepackage{amsmath}
 \usepackage{amsfonts}
 \usepackage{amssymb}
 \usepackage{graphicx}
 \usepackage{subfigure}
 \usepackage{enumerate}
 \usepackage{verbatim}% for \begin{comment} \end{comment}
 \usepackage{color}
 \usepackage{xcolor}
 \usepackage{bm}
 \usepackage[]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {red},
    citebordercolor = {green},
}
 \begin{document}
 \title{One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction}
 \author{Zhiyu}
 \affiliation{Fudan University, Shanghai, China}

@@

\section{Preparation}\label{section:preparation}
\subsection{Scaling behaviour}
We investigated the classical gas in harmonic trap with a repulsive interaction. We chose one of the simplest types of interaction:
\begin{equation}
F=\left\lbrace
\begin{aligned}
&F=F_0 	&,x\textless\sigma\\
&F=0 	&,x\textgreater\sigma
\end{aligned}
\right.
\label{eq:preparation1}
\end{equation}
so the Hamiltonian is
\begin{equation}
H=\frac{1}{2}m\omega_0^2\sum_{i}x_i^2+\frac{1}{2}m\sum_i v_i^2+\sum_{\left|x_i-x_j\right|\textless\sigma}F_0\left(\sigma-\left|x_i-x_j\right|\right)
\label{eq:preparation2}
\end{equation}
It can be shown that Eq.\ref{eq:preparation2} can be rewrite into the following form:
\begin{equation}
\tilde{H}=\frac{1}{2}\sum_{i}\tilde{x_i}^2+\frac{1}{2}\sum_i\left(\frac{d\tilde{x}}{d\tilde{t}}\right)^2+\sum_{\left|\tilde{x_i}-\tilde{x_j}\right|\textless 1}F_0\left(1-\left|\tilde{x_i}-\tilde{x_j}\right|\right)
\end{equation}
with the transformation:
\begin{equation}
\left\lbrace
\begin{aligned}
&\tilde{H}&=&\frac{H}{m\omega_0^2\sigma^2}\\
&\tilde{x_i}&=&\frac{x_i}{\sigma}\\
&\tilde{t}&=&\omega_0t\\
&\tilde{F_0}&=&\frac{F_0}{m\omega_0^2\sigma}\\
\end{aligned}
\right.
\end{equation}

@@

\subsection{Overview}
\subsubsection{Relation between Radius and Energy}
The radius of the cloud R is defined as the root-mean-square of particles' position $\left\lbrace x_i\right\rbrace$
\begin{equation}
R\equiv\left(\overline{x_i^2}\right)^\frac{1}{2}
\label{eq:def_of_R}
\end{equation}. When E is very large, the interaction energy can be omitted, so E is dominated by the kinetic energy and potential energy of harmonic oscillators. Thus, $E=\omega_0^2\sum_{i}x_i^2=N\omega_0^2R^2$

\subsubsection{Ground states}
For the ground state of this system, one could predict that \\(1) When the $\sigma$ is larger than the size of the cloud (in view of the scaling behaviour, large $\sigma$ is equivalent to small $F_0$ limit when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keeps an equal distance with its nearest neighbours, which is $\frac{2F_0}{\omega_0^2}$. The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When $F_0$ is very large the molecules act like a hardcore gas, while the size of particle is just $\sigma$.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_GS_pre_2_rev.eps}
\caption{particles' position at ground states }
\label{fig:GS1}
\end{figure}

@@

Since the number of particles we use in the Molecular Dynamics simulation is limited (usually 5 to 20), the random noise is significant. If we start with a state whose configuration in phase-space is an ellipse slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t). 
\begin{figure}[hbtp]
\center
\includegraphics[scale=0.32]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log_2_with_oscillation_demo.png}
\caption{breathing mode frequency measured at different E and $F_0$. Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation of radius R defined in Eq.\ref{eq:def_of_R}}
\label{fig:Breathingfrequency1}
\end{figure}

@@

Fig.\ref{fig:Breathingfrequency2_1} show this precession motion in the rotating frame in phase-space.

\begin{figure*}
\subfigure[$t=0$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=1-5T_rev.eps} 
\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=1-5T_rev.eps}
\end{minipage}
}
\subfigure[$t=\frac{1}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=2-5T_rev.eps} 
\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=2-5T_rev.eps}
\end{minipage}
}\subfigure[$t=\frac{2}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=3-5T_rev.eps} 
\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=3-5T_rev.eps}
\end{minipage}
}\subfigure[$t=\frac{3}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=4-5T_rev.eps} 
\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=4-5T_rev.eps}
\end{minipage}
}\subfigure[$t=\frac{4}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{D:/matlab2016/MolecularDynamics/figure/latexpic/stationary_frame_t=5-5T_rev.eps} 
\includegraphics[scale=0.22]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotating_frame_t=5-5T_rev.eps}
\end{minipage}
}
\caption{N=50,F0=100,E=50000. Upper(lower) five pictures are snapshot of the configuration of the cloud in the stationary(rotating) frame at t=$\frac{1}{5}T$, $\frac{2}{5}T$, $\frac{3}{5}T$, $\frac{4}{5}T$, $T$ respectively.}
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=0T_rev.eps} 
\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=20T_rev.eps}
\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=40T_rev.eps} 
\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=60T_rev.eps}
\includegraphics[scale=0.23]{D:/matlab2016/MolecularDynamics/figure/latexpic/10_18rotating_frame_t=80T_rev.eps} 
\caption{the precession behaviour of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
\label{fig:Breathingfrequency2_1}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_scanE_pre.eps}
\caption{dependence of breathing frequency on Energy, N=20. Different color stands for different $F_0$: {\color{red}{Red}} for $F_0$=2000; {\color{yellow}{Yellow}} for $F_0$=3000; {\color{green}{Green}} for $F_0$=10000;  {\color{blue}{Blue}} for $F_0$=100000. Run with 3 different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles). The black dashed line is the prediction of Eq.\ref{eq:breathingfrequency1}.}
\label{fig:Breathingfrequency4}
\end{figure}

The dependence of frequency on energy and $F_0$ is shown in fig.\ref{fig:Breathingfrequency4}. For the first thing, as expected when $F_0$ is high the frequency behaviour is well-described by linear prediction Eq.\ref{eq:breathingfrequency1}. Secondly, the figure shows the frequency's dependence on $F_0$. As we explained, when $F_0$ is not so large, the precession angle decrease. In language of real space, the finite $F_0$ create a finite approaching time, thus consumes the time saved by finite-range collision. As a result, the frequency should be lower when $F_0$ decrease, and reach 2 earlier.

@@

\begin{figure}[hbtp]
\centering
%\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
%\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_energydistribution_pre_rev.eps} 
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=10_energydistribution_pre_rev.eps} 
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_energydistribution_pre_rev.eps}
\caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, {\color{green}{green}} curves corresponds to Boltzmann distribution; {\color{red}{red}} curves are obviously non-Boltzmann, while the {\color{yellow}{yellow}} ones are intermediate case, represent ``thermalization threshold". In three figures for different N, we choose E/N identical (=1000), and thermalization is reached at $F_0=500$-$F_0=1000$, which is consistent with our prediction in Eq.\ref{eq:thermalizatiton condition}}
\label{fig:thermalization5}

@@

\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/boltzmann_N=10_F=10000_pre_rev.eps}
\caption{Energy distribution, N=10, F0=10000}
\label{fig:thermalization9}

\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/boltzmann_N=20_F=10000_pre_rev.eps} 
\caption{Energy distribution, N=20, F0=10000}
\label{fig:thermalization10}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_spectrum_N=10_E=1000_pre_rev.eps}
\caption{Frequency spectrum, measured over $10^4$ time units.\label{fig:frequencyspectrum}}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_screenshot.png}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_1_screenshot.png}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_2_screenshot.png}
\caption{LLE distribution for N=5, F0=1000, scan E.}
\label{fig:LLEdistribution1}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot_screenshot.png}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot1_screenshot.png}
\caption{``hot". top(bottom): default(modified)}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_parula_screenshot.png}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_parula1_screenshot.png}
\caption{``parula". top(bottom): default(modified)}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone_screenshot.png}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone1_screenshot.png}
\caption{``bone". top(bottom): default(modified)}
\end{figure}

@@

\begin{figure}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_1.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_2.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_3.png} 
\end{minipage}
}
\centering
\caption{Frequency of relative motion with internal energy in three regime} Numbers in the legend is the value of $\frac{F_0}{m\omega_0^2\sigma}$
\label{fig:thermalization3}
\end{figure}
\end{comment}

\bibliography{mybib}
